Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-05-02 ident_manu.Rnw
beth comments

We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}.

@@

% effects of changing initial and structural conditions
<<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in a 50\\% increase in parameter values. Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.  See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 6, fig.width = 4, out.width = '0.7\\textwidth', eval = T, echo = F, warning = F, message = F>>=
# initial conditions
data(ini_eval)
data(struct_eval)

@@

p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
  geom_point(aes(y = ave, shape = 'Ave', fill = 'Ave'), colour = lncol, size = sz) + 
  geom_point(aes(y = med, shape = 'Med', fill = 'Med'), colour = lncol, size = sz) + 
  scale_shape_manual(name = '', labels = c('Ave', 'Med'), values = c(21, 24)) + 
  scale_fill_manual(name = '', labels = c('Ave', 'Med'), values = cols[c(5, 3)]) +
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  mytheme %+replace%
  theme(legend.title = element_blank()) + 
  ggtitle('(b) By top parameters, all categories')

>>>>

We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}. We thank James Pauer, Yonghsan Wan, and Susan Elizabeth George for providing helpful comments on an earlier draft.

@@

% sensitivity heat map
<<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in a 50\\% increase in parameter values. Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.  See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 6, fig.width = 4, out.width = '0.7\\textwidth', eval = T, echo = F, warning = F, message = F>>=
# initial conditions
data(ini_eval)
data(struct_eval)

@@

p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
  geom_point(aes(y = ave, shape = 'Average', fill = 'Average'), colour = lncol, size = sz) + 
  geom_point(aes(y = med, shape = 'Median', fill = 'Median'), colour = lncol, size = sz) + 
  scale_shape_manual(name = '', labels = c('Average', 'Median'), values = c(21, 24)) + 
  scale_fill_manual(name = '', labels = c('Average', 'Median'), values = cols[c(5, 3)]) +
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  mytheme %+replace%
  theme(legend.title = element_blank()) + 
  ggtitle('(b) By top parameters, all categories')

### 2017-05-02 ident_manu.tex
beth comments

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Mon Apr 10 12:57:29 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/cb605034ebf62786fb3f412f99538ccdf606ffa4}{cb605034ebf62786fb3f412f99538ccdf606ffa4}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

@@

% effects of changing initial and structural conditions
\begin{figure}[!ht]

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Mon Apr 10 15:30:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/0f86dadf816bb11046b5ad72f427002e17bf4cef}{0f86dadf816bb11046b5ad72f427002e17bf4cef}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

@@

% sensitivity heat map
\begin{figure}[!ht]
